%% ----------------------------------------------------------------
%% AppendixC.tex
%% ---------------------------------------------------------------- 
\chapter{Questionnaire for Comparative Evaluation} \label{Chapter:Appendix C}

% Converted from Microsoft Word to LaTeX
% by Chikrii Softlab Word2TeX converter (version 5.0)
% Copyright (C) 1999-2011 Chikrii Softlab. All rights reserved.
% http://www.chikrii.com
% mailto: support@chikrii.com

% Warning: You are using Chikrii Softlab Word2TeX in TRIAL mode!
% In TRIAL mode some restrictions will apply.
% For more information please visit http://www.chikrii.com
% YOU CAN USE THIS FILE WITH THE SOLE PURPOSE OF EVALUATING Word2TeX.


\begin{center}
\textbf{Comparative Questionnaire for System Evaluation}
\end{center}

Question 1.1

Did you ever use any websites like UCAS or this one to search for 
universities or courses for your higher education? 

$\bigcirc $ Yes

$\bigcirc $ No

Question 1.2

Compared with UCAS, do you agree that the user interface of this website are 
easy to learn and understand? (1 $=$ Strongly disagree, 5 $=$ Strongly 
agree) 

$\bigcirc $ Strongly agree

$\bigcirc $ Agree

$\bigcirc $ Neutral

$\bigcirc $ Disagree

$\bigcirc $ Strongly disagree

Question 1.3

If you do not strongly agree, please describe any improvements in the 
interface and design should be considered. 

Question 1.4

Compared with UCAS, do you agree that the information of each part is 
helpful for your higher education destination choices? (1 $=$ Strongly 
disagree, 5 $=$ Strongly agree) 

\begin{table}[H]
\begin{center}
\begin{tabular}{|p{4cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
\hline
& 
1 & 
2 & 
3 & 
4 & 
5 \\
\hline
University {\&} Course& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $ \\
\hline
Ranking Table& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $ \\
\hline
Course Location& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $ \\
\hline
Weather & 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $ \\
\hline
Criminality& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $ \\
\hline
Infrastructure& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $& 
$\bigcirc $ \\
\hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}

Question 1.5

If you do not totally agree, please describe any improvements in information 
of each part should be considered.

Question 1.6

Compared with UCAS, do you agree that the overall user experience of this 
website is good? (1 $=$ Strongly disagree, 5 $=$ Strongly agree) 

$\bigcirc $ 1

$\bigcirc $ 2

$\bigcirc $ 3

$\bigcirc $ 4

$\bigcirc $ 5

Question 1.7

If you do not strongly agree, please describe any improvements in the 
overall user experience should be considered.

Question 1.8

Compared with UCAS, do you think this website is more helpful for you to 
decide your higher education destination choices? (1 $=$ Strongly disagree, 
5 $=$ Strongly agree) 

$\bigcirc $ 1

$\bigcirc $ 2

$\bigcirc $ 3

$\bigcirc $ 4

$\bigcirc $ 5

Question 1.9

If you do not totally agree, please explain the answer from above question 
to give further clarification.

Question 1.10

Are you willing to recommend this website to your friends or peers? 

$\bigcirc $ Yes

$\bigcirc $ No

Question 1.11

What additional information on the universities or cities would you like 
included on this website?

\begin{center}
\textbf{Thank you for taking this questionnaire.}
\end{center}

