%% ----------------------------------------------------------------
%% Thesis.tex
%% ---------------------------------------------------------------- 
\documentclass[oneside]{ecsthesis}      % Use the Thesis Style

\graphicspath{{../Figures/}}   % Location of your graphics files
\usepackage{natbib}            % Use Natbib style for the refs.
\hypersetup{colorlinks=true}   % Set to false for black/white printing
\input{Definitions}            % Include your abbreviations
\usepackage{booktabs}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{float}
\usepackage{rotating}
\usepackage{longtable} % for 'longtable' environment
\usepackage{pdflscape} % for 'landscape' environment
\usepackage{array} % for extrarowheight
\usepackage{latexsym}

%% ----------------------------------------------------------------
\begin{document}
\frontmatter
\title      {A Web Application Using Open Data and Data Visualisation for Higher Education Destination Choices in The UK}
\authors    {\texorpdfstring
             {\href{mailto:sw9n14@ecs.soton.ac.uk}{SHANCHUAN WU (sw9n14)}}
             {SHANCHUAN WU}
            }
            
     
%\supervisor {Dr. Mark J Weal}
\addresses  {\groupname\\\deptname\\\univname}
\date       {\today}
\subject    {}
\keywords   {}

\maketitle

\begin{abstract}
With the contemporary globalisation, the number of international students in the UK has risen strongly over the last decade. When international students choose universities and cities for their higher education, they will take many different factors into consideration. Therefore, international students’ higher education destination choice involves multiple factors. Some of these factors play a vital role in this decision-making process. There are many potential benefits of open data for higher education, and one of them is to help students make informed education decisions.  Data visualisation is a powerful tool to represent and analyse the data, so it becomes essential for decision making. 

This dissertation identified some significant factors that influence the decision-making process of international students in the UK for their higher education and implemented a web application to visualise open data about these factors. This web-based application proved to be helpful for international students when they decide destination cities and universities for their higher education in the UK.\end{abstract}
\tableofcontents
\listoffigures
\listoftables
%\lstlistoflistings
%\listofsymbols{ll}{$w$ & The weight vector}
\acknowledgements{I would like to express my deepest appreciation to my supervisor, Dr. Mark J Weal, for the continuous support of my dissertation and project, for his patience, motivation, and immense knowledge. His guidance helped me in all the time of project and writing of this dissertation.

Besides, I would like to thank my examiner, Dr. Elena Simperl, for her valuable advice and suggestions for my project and dissertation.

My sincerely thank also goes to my friends and classmates in University of Southampton. In particular, I am grateful to two of my best friends, Chunhui Zhou and Chaofeng Zhou, for enlightening me on system development.


Last but not the least, I would like to thank my family: my parents and brother for supporting me spiritually throughout writing this dissertation and my life in general.}
%\dedicatory{To \dots}
\mainmatter
%% ----------------------------------------------------------------
\include{Introduction}
\include{Background}
\include{Management}
\include{Analysis}
\include{Design}
\include{Implementation}
\include{Test}
\include{Conclusions}
%\bibliographystyle{ecs}
%\bibliography{ECS}

\appendix
\include{AppendixA}
\include{AppendixB}
\include{AppendixC}
\backmatter
\bibliographystyle{unsrt}
\bibliography{ECS}
\end{document}
%% ----------------------------------------------------------------